Detecting AI-Generated Images using ResNet

### 2022-12-14 paper/paper.tex
Update paper

% TODO: Placeholder for now, data not real
\begin{table*}
  \centering
  \begin{tabular}{c|c||c|c|c|c}
    \hline
    \textbf{Dataset} & \textbf{Model} & \textbf{Precision} & \textbf{Recall} & \textbf{F1-Score} & \textbf{Accuracy} \\
    \hline
    Indoor + SD & ResNet34       & {71.88\%}          & {61.33\%}       & {66.19\%}      & {71.88\%}    \\
    Indoor + SD & ResNet50           & {93.75\%}          & {90.00\%}       & {91.84\%}      & {71.88\%}    \\
    Weather + SD & ResNet34  & {93.19\%}          & {91.33\%}       & {92.25\%}       & {71.88\%}   \\
    Weather + SD & ResNet50       & {92.00\%}          & {92.00\%}       & {92.00\%}      & {71.88\%}    \\
    Comic + SD & ResNet34 & {92.00\%}          & {92.00\%}       & {92.00\%}      & {71.88\%}    \\
    Comic + SD & ResNet50 & {92.00\%}          & {92.00\%}       & {92.00\%}      & {71.88\%}    \\
    Small Indoor + DALLE2 & ResNet34 & {92.67\%}          & {92.67\%}       & {92.67\%}      & {71.88\%}    \\
    Small Indoor + DALLE2 & ResNet50 & {92.67\%}          & {92.67\%}       & {92.67\%}      & {71.88\%}    \\
    Weather + DALLE2 & ResNet34 & {92.67\%}          & {92.67\%}       & {92.67\%}      & {71.88\%}    \\
    Weather + DALLE2 & ResNet50 & {92.67\%}          & {92.67\%}       & {92.67\%}      & {71.88\%}    \\
    \hline
  \end{tabular}
  \caption{Precision, Recall and F1-Score on the \% datasets}
  \label{tab:results-on-datasets}
\end{table*}

>>>>

\begin{table*}
  \centering
  \begin{tabular}{c|c||c|c|c|c}
    \hline
    \textbf{Dataset}      & \textbf{Model} & \textbf{Accuracy} & \textbf{Precision} & \textbf{Recall} & \textbf{F1-Score} \\
    \hline
    Indoor + SD (train)   & ResNet34       & {98.99\%}         & {99.07\%}          & {98.72\%}       & {99.00\%}         \\
    Indoor + SD (train)   & ResNet50       & {98.51\%}         & {98.90\%}          & {98.10\%}       & {98.50\%}         \\
    \hline
    Weather + SD          & ResNet34       & {69.75\%}         & {63.46\%}          & {93.13\%}       & {75.48\%}         \\
    Weather + SD          & ResNet50       & {71.55\%}         & {64.65\%}          & {95.07\%}       & {76.97\%}         \\
    Comic + SD            & ResNet34       & {92.87\%}         & {88.58\%}          & {98.44\%}       & {93.25\%}         \\
    Comic + SD            & ResNet50       & {98.34\%}         & {100.00\%}         & {96.68\%}       & {98.31\%}         \\
    Small Indoor + DALLE2 & ResNet34       & {51.04\%}         & {80.95\%}          & {2.72\%}        & {5.27\%}          \\
    Small Indoor + DALLE2 & ResNet50       & {51.84\%}         & {82.86\%}          & {4.65\%}        & {8.80\%}          \\
    Weather + DALLE2      & ResNet34       & {50.83\%}         & {53.33\%}          & {13.33\%}       & {21.33\%}         \\
    Weather + DALLE2      & ResNet50       & {50.67\%}         & {56.67\%}          & {5.67\%}        & {10.30\%}         \\
    \hline
  \end{tabular}
  \caption{Precision, Recall and F1-Score on the \% datasets}
  \label{tab:results-on-datasets}
\end{table*}
